### 2021-02-01 博士/毕业论文/ucasthesis/Tex/Chap_MTP.tex
将 MTP 翻译成中文

\chapter{Manipulating Template Pixels for Model Adaptation of Siamese Visual Tracking}\label{chap:MTP}

\section{Abstract}
In this letter, we show that the challenging model adaptation task in visual object tracking can be handled by simply manipulating pixels of the template image in Siamese networks. For a target that is not included in the offline training set, a slight modification of the template image pixels will improve the prediction result of the offline trained Siamese network. The popular adversarial example generation methods can be used to perform template pixel manipulation for model adaptation. Different from current template update methods, which aim to combine the target features from previous frames, we focus on the initial adaptation using target ground-truth in the first frame. Our model adaptation method is pluggable, in the sense that it does not alter the overall architecture of its base tracker. To our knowledge, this work is the first attempt to directly manipulating template pixels for model adaptation in Siamese-based trackers. Extensive experiments on recent benchmarks demonstrate that our method achieves better performance than some other state-of-the-art trackers. Our code is available at https://github.com/lizhenbang56/MTP.

\section{Introduction}
Object tracking refers to the task of sequentially locating a specified moving object in a video, given only its initial state. Recently, Siamese networks \cite{danelljan2019atom, bertinetto2016fully} have demonstrated a significant improvement in object tracking performances. Siamese trackers formulate the visual object tracking problem as learning cross-correlation similarities between a target template and a search region. Tracking is then performed by finding the target object from the search image region by computing the highest visual similarity. Despite its recent success, the learned similarity measure of the Siamese network is not necessarily reliable for objects that are not included in the offline training set, leading to poor generalization \cite{Bhat_2019_ICCV}. Several recent works aim to adapt the model to the current target appearance. For example, TADT \cite{Li_2019_CVPR} identifies the importance of each convolutional filter according to the back-propagated gradients and selects the target-aware features based on activations for representing the targets. However, the feature extractor of TADT is pre-trained on ImageNet \cite{russakovsky2015imagenet}, not on large-scale visual tracking datasets. This limits the representation ability of its features on the object tracking task. GradNet \cite{Li_2019_ICCV} exploits the discriminative information in gradients and updates the template in the Siamese network through feed-forward and backward operations. However, the extra sub-network increases the computational cost and is prone to overfitting. UpdateNet \cite{Zhang_2019_ICCV} learns to combine the target features from previous frames. However, it does not use ground truth information to adaptively adjust the template features of the first frame.

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/MTP/got10k/visulization2.pdf}
    \caption{A comparison of our method with the state-of-the-art trackers ATOM \cite{danelljan2019atom} and SiamFCv2 \cite{bertinetto2016fully} in challenging situations. The example frames are from the GOT-10k \cite{huang2018got} testing set.}
    %\caption{A comparison of our method with ATOM \cite{danelljan2019atom} and SiamFCv2 \cite{bertinetto2016fully}. The example frames are from the GOT-10k \cite{huang2018got} testing set.}
    \label{fig:vis}
\end{figure}

In this work, we show that the challenging model adaptation task in visual object tracking can be handled by simply manipulating pixels of the template image in Siamese networks. Given an object tracker, our algorithm modifies template pixels in only a few gradient-descent iterations using the target ground-truth in the first frame. For a target that is not included in the offline training set, we believe that a slight modification of the template image pixels can improve the prediction result of the offline trained Siamese network. We use the adversarial example generation method to achieve this, because it is commonly used to slightly modify the input image, and thereby impose an impact on the prediction result of the network. We depart from the purpose of adversarial sample generating in that the latter is aimed to make the prediction of the network worse, while we hope the prediction of the Siamese network is better. The proposed model adaptation method can be integrated with varieties of Siamese trackers like SiamFC++ \cite{SiamFC++}. Note that the parameters of the Siamese network remain intact to preserve the generative ability of offline-trained embedding space. We perform comprehensive experiments on 4 tracking benchmarks: VOT2018\cite{kristan2018sixth}, TrackingNet\cite{muller2018trackingnet}, GOT-10k\cite{huang2018got}, and OTB2015\cite{wu2013online}. Our approach achieves state-of-the-art results while running at over 80 FPS (see Fig. \ref{fig:vis}).

\section{Proposed Algorithm}
In this section, we present a new model adaptation approach for Siamese trackers via directly manipulating template pixels. We start by revisiting the tracking process of popular template matching-based trackers, which is closely related to the proposed approach. Following \cite{Danelljan_2020_CVPR}, we formulate object tracking as a confidence-based regression problem, which learns a function $s_\theta:\mathcal{Y\times X\rightarrow \mathbb R}$, and predicts a scalar confidence score $s_\theta(y,x)\in\mathbb R$ given an output-input pair $(y,x)$. The final estimate $f(x)=y^*$ is predicted as follows:
\begin{equation}
    f(x) = \arg\max_{y\in \mathcal Y}s_\theta (y,x),
\end{equation}
where $x$ is an input image. $y$ usually represents the center 2D image coordinate of the target object. Currently, there are two prevalent template matching-based paradigms: discriminative correlation filter (DCF) approaches and Siamese tracking methods.

In DCF-based methods, a circular correlation filter $w_{\theta}$ is trained during tracking to predict a target confidence score:
\begin{equation}
    s_\theta(y,x)=(w_\theta * \phi(x))(y),
    \label{equ:dcf}
\end{equation}
where $\phi(x)$ is the features extracted from the search image $x$.

In contrast to DCF, Siamese trackers exploit a two-stream architecture. One stream extracts the target’s features $\phi_\theta(z)$ based on the template image $z$ which is cropped from the first frame according to the ground truth bounding box. The other stream receives as input a large search image $x$ and outputs the search features $\phi_\theta(x)$. The two outputs are cross-correlated to predict a target confidence score:
\begin{equation}
    s_\theta(y,x)=(\phi_\theta(z) * \phi_\theta(x))(y).
    \label{equ:siamese}
\end{equation}

DCF-based trackers and Siamese trackers both have the advantage of utilizing large-scale visual tracking datasets to train the feature extractor $\phi(\cdot)$ or the embedding network $\phi_{\theta}(\cdot)$ by their own right. This way the representation ability of features on the object tracking task can be enhanced.

In contrast to Siamese trackers, DCF learns the filter $w_\theta$ from example patches of the target appearance to discriminate it from the background.
Despite the improved tracking efficiency using the circular correlation operation, its boundary effect and sophisticated optimization prevent itself from making a good trade-off between computational speed and tracking performance. Siamese trackers do better in this aspect, although the learned similarity measure in the cross-correlation is not necessarily reliable for objects that are not included in the offline training set, leading to poor generalization.

In this letter, we aim to design a new Siamese tracking method that has the ability to make full use of the specific information of the current video for model adaptation like the DCF-based trackers, although the object in it is not included in the offline training set. This is achieved by utilizing the annotation information in the first frame to perform model adaptation.

Note that Equ. (\ref{equ:dcf}) and Equ. (\ref{equ:siamese}) bear some similarities with each other, and the main difference lies in the kernel term for correlation: the kernel of DCF is the online-learned $w_{\theta}$, and the kernel of the Siamese network is $\phi_\theta(z)$. In order for the Siamese network to have the model adaptation ability, we need to adapt $\phi_\theta(z)$ using the first frame ground truth annotation of the current video. There are two design choices to adapt $\phi_\theta(z)$: changing $\phi_\theta(\cdot)$ or changing $z$. However, changing $\phi_\theta(\cdot)$ may cause too much tedious meta-learning settings to ensure the generative ability of offline-trained embedding space \cite{ROAM, DBLP:conf/aaai/JungYNCH20}. In contrast, our solution is in a simple way to perform model adaptation of Siamese trackers by changing $z$, i.e., modifying template pixels in only a few gradient-descent iterations using the target ground-truth at the first frame. Compared with current model adaptation methods of Siamese trackers, the proposed method has the following advantages. First, we never modify parameters of the Siamese network to preserve the representation ability of offline-trained embedding space. Second, different from current template update methods \cite{zhu2018distractor, Zhang_2019_ICCV}, which aim to combine the target features from previous frames, we focus on the initial adaptation using target ground-truth at the first frame. Finally, our model adaptation method is pluggable, in the sense that it does not alter the overall architecture of the base tracker. In the next subsection, we will show how the popular adversarial example generation methods can be used to perform template pixel manipulation for model adaptation.

\subsection{Manipulating Template Pixels for Model Adaptation}
At first glance, there may be a contradiction between the model adaptation task and the adversarial example generation task, because these two tasks have different purposes. An adversarial example \cite{kurakin2017adversarial} is a sample of input data which has been modified very slightly in a way that is intended to perform an attack on machine learning systems, which means to cause a machine learning model to make wrong predictions. However, the purpose of model adaptation in our work is to make full use of the annotation information in the first frame to improve the tracking performance for the current video. We will point out in the following that there are some similarities between these two tasks and we can utilize adversarial example generation methods to perform the model adaptation task.

Before introducing the proposed method, we first revisit the popular adversarial example generation methods. One of the simplest methods to generate adversarial images $I^{adv}$ works by linearizing loss function in $L_{\infty}$ neighbourhood of a clean image and finds exact maximum of linearized function using following closed-form equation \cite{FGSM}:
\begin{equation}
    I^{adv} = I + \epsilon \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
\end{equation}
where $I$ is the input image, and the values of the pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$. $L(I, y)$ is the cost function of the neural network for the attack purpose, given image $I$ and label $y$. $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size, and clipping pixel values of intermediate results after each step to ensure that they are in an $\epsilon$-neighbourhood of the original image.  This leads to the Basic Iterative Method (BIM) introduced in \cite{kurakin2017adversarial}: 
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I,\epsilon}\{I_N^{adv}+\alpha \text{ sign}(\nabla_I L(I_N^{adv},y_{true}))\},
    \end{gathered}
\end{equation}
where $Clip_{I, \epsilon} \left\{ I' \right\}$ is the function which performs per-pixel clipping of the image $I'$, so that the result will be in $L_{\infty}$ $\epsilon$-neighbourhood of the source image $I$.
The BIM can be easily made into an attacker for a specific desired target class, called the Iterative Target Class Method \cite{kurakin2017adversarial}:
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I,\\
        I_{N+1}^{adv} = Clip_{I,\epsilon}\{I_N^{adv}-\alpha \text{ sign}(\nabla_I L(I_N^{adv},y_{target}))\}.
    \end{gathered}
    \label{equ:itcm}
\end{equation}
Equ. (\ref{equ:itcm}) shows that manipulating pixels of the input image in only a few gradient-descent iterations is able to change the network's prediction to the target class $y_{target}$. Note that our purpose is manipulating pixels of the template image in the first frame, so that the prediction is closer to the ground truth bounding box. So we can perform model adaptation for Siamese networks using Equ. (\ref{equ:itcm}) with some modifications:
\begin{equation}
    \begin{gathered}
        z_0 = z,\\
        z_{N+1} = Clip_{z,\epsilon}\{z_N -\alpha \text{ sign}(\nabla_z L(z_N,y_{bb}))\},
    \end{gathered}
    \label{equ:adaptaion}
\end{equation}
where $z$ is the template image in the first frame, and $y_{bb}$ is the label for Siamese trackers generated from the ground truth bounding box. In the next subsection, we will introduce the overall tracking process equipped with the proposed model adaptation module.

%%%%%%%%%%%%%%%%
\begin{table}[t]
\renewcommand\arraystretch{0.8}
\caption{State-of-the-art comparison on the popular tracking benchmark OTB2015 with the running speed. FPS: frame per second. Our speed is tested on an NVIDIA RTX 2080Ti GPU.}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l | c c c c c c}
\toprule
Trackers & ECO & MDNet & SiamRPN++ & ATOM & SiamFC++\_G & Ours \\
\midrule
Success & 70.0 & 67.8  & 69.6      & 66.9      & 68.3       & 69.7 \\
FPS     & 8    & 1     & 35        & 30       & 90         & 82  \\
\bottomrule
\end{tabular}
\end{center}
\label{table:otb}
\end{table}
%%%%%%%%%%%

%%%%%%%%%%%%%%%%
\begin{table}[t]
\renewcommand\arraystretch{0.8}
\centering
\caption{state-of-the-art comparison on the TrackingNet test dataset in terms of precision, normalized precision and success.}
\begin{tabular}{l c c c}
\toprule
Method   &  Prec.   &  Norm. Prec. & Succ.  \\
\midrule
Ours  &  70.6&  81.7 &74.9 \\
SiamFC++\_G& 70.5 & 80.0 & 75.4 \\
SiamFC++\_A  & 64.6 & 75.8 & 71.2 \\
ATOM              & 64.8 & 77.1 & 70.3 \\
SiamRPN++&  69.4 & 80.0 &73.3 \\
MDNet	 &  56.5&  70.5 &60.6 \\
ECO	 &  49.2&  61.8 &55.4 \\
SiamFC	 &  51.8&  65.2 &55.9 \\
\bottomrule
\end{tabular}
\label{tabel:trackingnet}
\end{table}
%%%%%%%%%%%

%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/MTP/got10k/success_plot.png}
    \caption{Comparing the results of our approach against other approaches over the GOT-10k test set. The trackers are ranked by their average overlap scores.}
    \label{fig:got10k}
\end{figure}
%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tracking Framework}
The proposed model adaptation method is integrated with the SiamFC++ tracker \cite{SiamFC++} in a plug-and-play manner. SiamFC++ is based on SiamFC \cite{bertinetto2016fully} and progressively refined according to several guidelines proposed in \cite{SiamFC++}. The input of the original SiamFC++ network is composed of the template image $z_0$ cropped from the first frame and search image $x_i$ cropped from the $i$-th frame. However, we expect to perform template manipulating such that, after $N$ steps of pixel update on the input pair $(z_0, x_0)$ to obtain $z'$, the tracker performs well on $(z', x_i)$. To achieve this, we start by cropping the initial template image $z_0\in\mathbb R^{3\times128\times 128}$ and the initial search image $x_0\in\mathbb R^{3\times289\times 289}$ from the first frame using the ground truth bounding box.
Then, $z_0$ and $x_0$ are sent to the SiamFC++ network to obtain the tracking prediction of the first frame. The tracking loss in SiamFC++ \cite{SiamFC++} is calculated as follows:
\begin{equation}
    L = L_{\text{cls}} + L_{\text{quality}} + L_{\text{reg}},
\end{equation}
where $L_{\text{cls}}$ is the focal loss \cite{lin2017focal}. $L_{\text{quality}}$ is the binary cross entropy (BCE) loss for quality assessment. $L_{reg}$ is the IoU loss \cite{yu2016unitbox} for bounding box regression. The gradient with respect to the template $z_0$ is used to generate $z_1$ according to Equ. (\ref{equ:adaptaion}). The updated template $z'$ is obtained by applying a very small number of iterations of Equ. (\ref{equ:adaptaion}). Note that the template image is only updated with the first frame of given sequences and is kept fixed during the whole tracking process to ensure stability.
The subsequent tracking procedure remains the same as SiamFC++.

@@

%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
In this section, we first present the implementation details. Then we compare our method with the state-of-the-art trackers on four tracking datasets: OTB2015 \cite{wu2013online}, VOT2018 \cite{kristan2018sixth}, GOT-10k \cite{huang2018got} and TrackingNet \cite{muller2018trackingnet}. Specifically, OTB2015 \cite{wu2013online} includes 100 sequences, which are labeled with different attributes for in-depth analysis of tracking performance. VOT2018 \cite{kristan2018sixth} uniquely applies a reset-based methodology and specially selects 60 sequences of various tracking scenarios for evaluation. GOT-10k \cite{huang2018got} and TrackingNet \cite{muller2018trackingnet} are two recent large-scale high-diversity datasets. They both cover diverse object classes and scenes in the train and test splits. For GOT-10k, there is no overlap in object classes between the train and test splits, promoting the importance of generalization to unseen object classes.

%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/MTP/vot18/vot18_eao.png}
    \caption{Expected average overlap graph with trackers ranked from right to left. The right-most tracker is the top-performing according to the VOT2018 expected average overlap values.}
    \label{fig:eao}
\end{figure}
%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation Details}
We use SiamFC++ \cite{SiamFC++} as our base tracker, and the backbone Siamese network adopts GoogLeNet \cite{szegedy2015going}. We do not perform any changes except for the model adaptation component. The parameter $\alpha$ in Equ. (\ref{equ:adaptaion}) is set to 0.05. Our method is implemented in Python with PyTorch. The proposed tracker runs at over 80 FPS on an NVIDIA RTX 2080Ti GPU.

>>>>

\chapter{为暹罗视觉跟踪的模型调整操作模板像素}\label{chap:MTP}

\section{摘要}
在这封信中，我们表明可以通过简单地在连体网络中操纵模板图像的像素来处理视觉对象跟踪中具有挑战性的模型自适应任务。对于不包含在离线训练集中的目标，模板图像像素的稍加修改将改善离线训练的暹罗网络的预测结果。流行的对抗性示例生成方法可用于执行模板像素操作以进行模型调整。与当前的模板更新方法（旨在合并先前帧的目标特征）不同，我们专注于在第一帧中使用目标地面真实性进行初始自适应。我们的模型调整方法是可插拔的，因为它不会改变其基本跟踪器的总体架构。据我们所知，这项工作是直接操纵模板像素以在基于暹罗的跟踪器中进行模型调整的首次尝试。在最近的基准测试中进行的大量实验表明，我们的方法比其他一些最新的跟踪器具有更好的性能。我们的代码可从https://github.com/lizhenbang56/MTP获得。

\section{简介}
对象跟踪是指仅在指定初始对象的初始状态下，在视频中顺序定位指定运动对象的任务。最近，暹罗网络 \cite{danelljan2019atom, SiamFC} 已经证明了对象跟踪性能的显着提高。暹罗跟踪器将视觉对象跟踪问题公式化为学习目标模板和搜索区域之间的互相关相似性。然后，通过计算最高的视觉相似度，从搜索图像区域中找到目标对象，从而进行跟踪。尽管最近取得了成功，但对于不包含在离线训练集中的对象，所学习的暹罗网络相似度度量不一定可靠，从而导致泛化效果较差 \cite{Bhat_2019_ICCV}。最近的一些工作旨在使模型适应当前的目标外观。例如，TADT \cite{Li_2019_CVPR} 根据反向传播的梯度识别每个卷积滤波器的重要性，并基于用于表示目标的激活来选择目标感知特征。但是，TADT的特征提取器是在ImageNet \cite{VID}上而不是在大规模视觉跟踪数据集上进行预训练的。这限制了其功能在对象跟踪任务上的表示能力。GradNet \cite{Li_2019_ICCV} 利用渐变中的区别信息，并通过前馈和后退操作更新暹罗网络中的模板。但是，额外的子网会增加计算成本，并且容易过度拟合。 UpdateNet \cite{Zhang_2019_ICCV} 学习合并先前框架中的目标功能。但是，它不使用地面真实信息来自适应地调整第一帧的模板特征。

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/MTP/got10k/visulization2.pdf}
    \caption{我们的方法与最先进的跟踪器 ATOM \cite{danelljan2019atom} 和SiamFCv2 \cite{SiamFC} 的比较。示例帧来自GOT-10k \cite{GOT-10k} 测试集。}
    %\caption{A comparison of our method with ATOM \cite{danelljan2019atom} and SiamFCv2 \cite{SiamFC}. The example frames are from the GOT-10k \cite{GOT-10k} testing set.}
    \label{fig:vis}
\end{figure}

在这项工作中，我们表明视觉对象跟踪中具有挑战性的模型适应任务可以通过简单地在连体网络中操纵模板图像的像素来处理。给定一个对象跟踪器，我们的算法仅使用第一帧中的目标地面真相，仅在几次梯度下降迭代中修改模板像素。对于不包含在离线训练集中的目标，我们认为对模板图像像素进行略微修改可以改善离线训练的暹罗网络的预测结果。我们使用对抗性示例生成方法来实现此目的，因为它通常用于略微修改输入图像，从而对网络的预测结果产生影响。我们偏离对抗性样本生成的目的，因为后者旨在使网络预测变得更糟，而我们希望暹罗网络的预测更好。提出的模型自适应方法可以与各种Siamese跟踪器（如SiamFC ++ \cite{SiamFC++}）集成。请注意，暹罗网络的参数保持完整，以保留离线训练的嵌入空间的生成能力。我们对4个跟踪基准进行了全面的实验：VOT2018\cite{kristan2018sixth}，TrackingNet\cite{muller2018trackingnet}，GOT-10k\cite{GOT-10k} 和 OTB2015\cite{OTB}. 我们的方法实现了最好的结果，同时以超过80 FPS的速度运行（见图 \ref{fig:vis}）。

\section{拟议算法}
在本节中，我们将通过直接操纵模板像素为暹罗跟踪器提供一种新的模型自适应方法。我们首先回顾与基于模板匹配的流行跟踪器的跟踪过程，这与所提出的方法密切相关。遵循 \cite{Danelljan_2020_CVPR}，我们将对象跟踪公式化为基于置信度的回归问题，该问题学习函数 $s_\theta:\mathcal{Y\times X\rightarrow \mathbb R}$，并预测标量置信度得分 $s_\theta(y,x)\in\mathbb R$ 给定一个输出-输入对 $(y,x)$。最终估计 $f(x)=y^*$ 预测如下：
\begin{equation}
    f(x) = \arg\max_{y\in \mathcal Y}s_\theta (y,x),
\end{equation}
其中 $x$ 是输入图像。$y$ 通常表示目标对象的中心2D图像坐标。当前，有两种流行的基于模板匹配的范例：判别相关滤波器（DCF）方法和暹罗跟踪方法。

在基于DCF的方法中，在跟踪过程中训练了圆形相关滤波器 $w_{\theta}$ 来预测目标置信度得分：
\begin{equation}
    s_\theta(y,x)=(w_\theta * \phi(x))(y),
    \label{equ:dcf}
\end{equation}
其中 $\phi(x)$ 是从搜索图像 $x$ 中提取的特征。

与DCF相比，暹罗跟踪器采用两流体系结构。一个流根据模板图像 $z$ 提取目标的特征 $\phi_\theta(z)$ ，该模板图像是根据地面真实边界框从第一帧裁剪而来的。另一个流接收较大的搜索图像 $x$ 作为输入，并输出搜索特征 $\phi_\theta(x)$。这两个输出互相关以预测目标置信度得分：
\begin{equation}
    s_\theta(y,x)=(\phi_\theta(z) * \phi_\theta(x))(y).
    \label{equ:siamese}
\end{equation}

基于DCF的跟踪器和暹罗跟踪器都具有利用大规模视觉跟踪数据集来训练特征提取器 $\phi(\cdot)$ 或嵌入网络 $\phi_{\theta}(\cdot)$ 的优势。自己的权利。这样，可以增强特征在对象跟踪任务上的表示能力。

与暹罗跟踪器相反，DCF从目标外观的示例补丁中学习过滤器 $w_\theta$ ，以将其与背景区分开。
尽管使用了循环相关运算提高了跟踪效率，但其边界效应和复杂的优化却无法在计算速度和跟踪性能之间做出良好的权衡。暹罗跟踪器在这方面做得更好，尽管在互相关中学习到的相似性度量对于未包含在离线训练集中的对象不一定是可靠的，从而导致通用性差。

在这封信中，我们旨在设计一种新的暹罗跟踪方法，该方法可以像基于DCF的跟踪器一样充分利用当前视频的特定信息进行模型调整，尽管其中的对象不包含在离线环境中训练集。这是通过利用第一帧中的注释信息执行模型调整来实现的。

注意等式 \ref{equ:dcf} 和等式 \ref{equ:siamese} 彼此之间有一些相似之处，主要区别在于相关性的内核术语：DCF的内核是在线学习的 $w_{\theta}$ ，而连体网络是 $\phi_\theta(z)$。为了使暹罗网络具有模型自适应能力，我们需要使用当前视频的第一帧地面真相注释来自适应 $\phi_\theta(z)$。适应 $\phi_\theta(z)$ 有两种设计选择：更改 $\phi_\theta(\cdot)$ 或更改 $z$。但是，更改 $\phi_\theta(\cdot)$ 可能会导致繁琐的元学习设置，无法确保脱机训练的嵌入空间 \cite{ROAM, DBLP:conf/aaai/JungYNCH20}的生成能力。相反，我们的解决方案是以简单的方式通过更改 $z$来执行暹罗跟踪器的模型适配，即在第一帧使用目标地面真相仅在几次梯度下降迭代中修改模板像素。与当前的暹罗跟踪器模型自适应方法相比，该方法具有以下优点。首先，我们从不修改暹罗网络的参数来保留离线训练的嵌入空间的表示能力。其次，与当前模板更新方法 \cite{zhu2018distractor, Zhang_2019_ICCV} 不同，该方法旨在合并先前帧的目标特征，我们专注于在第一帧使用目标地面真实性进行初始自适应。最后，在不改变基本跟踪器整体架构的意义上，我们的模型自适应方法是可插拔的。在下一个小节中，我们将展示如何使用流行的对抗性示例生成方法来执行用于模型自适应的模板像素操作。

\subsection{调整模板像素以进行模型调整}
乍一看，模型适应任务与对抗性示例生成任务之间可能存在矛盾，因为这两个任务具有不同的目的。一个对抗示例 \cite{kurakin2017adversarial} 是输入数据的一个示例，该示例已进行了很小的修改，目的是对机器学习系统进行攻击，这意味着导致机器学习模型做出错误的预测。但是，我们工作中模型自适应的目的是在第一帧中充分利用注释信息，以提高当前视频的跟踪性能。在下文中，我们将指出这两个任务之间存在一些相似之处，并且我们可以利用对抗性示例生成方法来执行模型自适应任务。

在介绍提出的方法之前，我们首先回顾流行的对抗性示例生成方法。生成对抗图像 $I^{adv}$ 的最简单方法之一是通过线性化干净图像的 $L_{\infty}$ 邻域中的损失函数，并使用以下闭式方程 \cite{FGSM}：
\begin{equation}
    I^{adv} = I + \epsilon \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
\end{equation}
其中 $I$ 是输入图像，像素值是[0，255]范围内的整数。 $y_{true}$ 是图像 $I$ 的真实标签。给定图像 $I$ 和标签 $y$，$L(I, y)$ 是用于攻击目的的神经网络的成本函数。 $\epsilon$ 是要选择的超参数。扩展上述方法的一种直接方法是，以较小的步长多次应用它，并在每个步骤之后裁剪中间结果的像素值，以确保它们位于原始图像的 $\epsilon$ 邻域中。这导致在 \cite{kurakin2017adversarial} 中引入了基本迭代方法（BIM）：
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I,\epsilon}\{I_N^{adv}+\alpha \text{ sign}(\nabla_I L(I_N^{adv},y_{true}))\},
    \end{gathered}
\end{equation}
其中 $Clip_{I, \epsilon} \left\{ I' \right\}$ 是对图像 $I'$ 进行逐像素裁剪的函数，因此结果将在源图像 $I$ 的$L_{\infty}$ $\epsilon$ 邻域内。
BIM可以很容易地变成特定期望目标类的攻击者，称为迭代目标类方法 \cite{kurakin2017adversarial}：
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I,\\
        I_{N+1}^{adv} = Clip_{I,\epsilon}\{I_N^{adv}-\alpha \text{ sign}(\nabla_I L(I_N^{adv},y_{target}))\}.
    \end{gathered}
    \label{equ:itcm}
\end{equation}
等式 \ref{equ:itcm} 表明，仅需进行几次梯度下降迭代操作就可以将输入图像的像素更改为目标类 $y_{target}$。请注意，我们的目的是在第一帧中处理模板图像的像素，以便使预测更接近于地面真实边界框。因此，我们可以使用等式 \ref{equ:itcm} 对暹罗网络进行模型自适应进行一些修改：
\begin{equation}
    \begin{gathered}
        z_0 = z,\\
        z_{N+1} = Clip_{z,\epsilon}\{z_N -\alpha \text{ sign}(\nabla_z L(z_N,y_{bb}))\},
    \end{gathered}
    \label{equ:adaptaion}
\end{equation}
其中 $z$ 是第一帧中的模板图像，而 $y_{bb}$ 是从地面真相边界框生成的暹罗跟踪器的标签。在下一个小节中，我们将介绍配备了建议的模型自适应模块的整体跟踪过程。

%%%%%%%%%%%%%%%%
\begin{table}[t]
\renewcommand\arraystretch{0.8}
\caption{与流行的跟踪基准OTB2015的最新运行速度进行比较。 FPS：每秒帧数。我们的速度已经在NVIDIA RTX 2080Ti GPU上进行了测试。}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l | c c c c c c}
\toprule
Trackers & ECO & MDNet & SiamRPN++ & ATOM & SiamFC++\_G & Ours \\
\midrule
Success & 70.0 & 67.8  & 69.6      & 66.9      & 68.3       & 69.7 \\
FPS     & 8    & 1     & 35        & 30       & 90         & 82  \\
\bottomrule
\end{tabular}
\end{center}
\label{table:otb}
\end{table}
%%%%%%%%%%%

%%%%%%%%%%%%%%%%
\begin{table}[t]
\renewcommand\arraystretch{0.8}
\centering
\caption{在TrackingNet测试数据集上的精度，标准化精度和成功方面的最新比较。}
\begin{tabular}{l c c c}
\toprule
Method   &  Prec.   &  Norm. Prec. & Succ.  \\
\midrule
Ours  &  70.6&  81.7 &74.9 \\
SiamFC++\_G& 70.5 & 80.0 & 75.4 \\
SiamFC++\_A  & 64.6 & 75.8 & 71.2 \\
ATOM              & 64.8 & 77.1 & 70.3 \\
SiamRPN++&  69.4 & 80.0 &73.3 \\
MDNet	 &  56.5&  70.5 &60.6 \\
ECO	 &  49.2&  61.8 &55.4 \\
SiamFC	 &  51.8&  65.2 &55.9 \\
\bottomrule
\end{tabular}
\label{tabel:trackingnet}
\end{table}
%%%%%%%%%%%

%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/MTP/got10k/success_plot.png}
    \caption{将我们的方法的结果与GOT-10k测试集上的其他方法进行比较。跟踪器按其平均重叠分数排名。}
    \label{fig:got10k}
\end{figure}
%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{跟踪框架}
所提出的模型自适应方法以即插即用的方式与SiamFC ++跟踪器 \cite{SiamFC++} 集成在一起。 SiamFC ++基于SiamFC \cite{SiamFC} ，并根据 \cite{SiamFC++}中提出的一些准则逐步完善。原始SiamFC ++网络的输入由从第一帧裁剪的模板图像 $z_0$ 和从第 $i$ 帧裁剪的搜索图像 $x_i$ 组成。但是，我们希望执行模板操作，以便在对输入对 $(z_0, x_0)$ 进行像素更新的 $N$ 个步骤后获得 $z'$，跟踪器在 $(z', x_i)$上表现良好。为此，我们首先裁剪初始模板图像 $z_0\in\mathbb R^{3\times128\times 128}$ 和初始搜索图像 $x_0\in\mathbb R^{3\times289\times 289}$ 使用地面真值边界框从第一帧开始。
然后，将 $z_0$ 和 $x_0$ 发送到SiamFC ++网络以获得第一帧的跟踪预测。 SiamFC ++ \cite{SiamFC++} 中的跟踪损耗计算如下：
\begin{equation}
    L = L_{\text{cls}} + L_{\text{quality}} + L_{\text{reg}},
\end{equation}
其中 $L_{\text{cls}}$ 是焦点损失 \cite{focal}. $L_{\text{quality}}$ 是用于质量评估的二进制交叉熵（BCE）损失。 $L_{reg}$ 是包围盒回归的IoU损失 \cite{yu2016unitbox} 。根据等式，相对于模板 $z_0$ 的梯度用于生成 $z_1$。 （公式 \ref{equ:adaptaion}）。 通过应用极少量的迭代可以获得更新的模板 $z'$（等式 \ref{equ:adaptaion}）。请注意，模板图片仅使用给定序列的第一帧进行更新，并在整个跟踪过程中保持固定以确保稳定性。
后续跟踪过程与SiamFC ++相同。

@@

%%%%%%%%%%%%%%%%%%%%%
\section{实验}
在本节中，我们首先介绍实现细节。然后，我们将我们的方法与四个跟踪数据集上的最新跟踪器进行比较：OTB2015 \cite{OTB}，VOT2018 \cite{kristan2018sixth}，GOT-10k \cite{GOT-10k} 和 TrackingNet \cite{muller2018trackingnet}。 具体来说，OTB2015 \cite{OTB} 包含100个序列，这些序列标记有不同的属性，用于深入分析跟踪性能。VOT2018 \cite{kristan2018sixth} 独特地应用了基于重置的方法，并特别选择了60种序列的各种跟踪方案进行评估。GOT-10k \cite{GOT-10k} 和 TrackingNet \cite{muller2018trackingnet} 是最近的两个大规模的高多样性数据集。它们都涵盖了火车和测试区中的各种对象类和场景。对于GOT-10k，训练和测试拆分之间的对象类别没有重叠，从而提高了对看不见的对象类别进行泛化的重要性。

%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/MTP/vot18/vot18_eao.png}
    \caption{预期的平均重叠图，跟踪器的排名从右到左。根据VOT2018预期的平均重叠值，最右边的跟踪器是效果最好的跟踪器。}
    \label{fig:eao}
\end{figure}
%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{实施细节}
我们使用SiamFC ++ \cite{SiamFC++}作为基本跟踪器，而主干Siamese网络采用GoogLeNet \cite{GoogLeNet}。除了模型调整组件，我们不执行任何更改。等式 \ref{equ:adaptaion} 中的参数 $\alpha$ 设为 0.05。我们的方法是使用PyTorch在Python中实现的。拟议的跟踪器在NVIDIA RTX 2080Ti GPU上以超过80 FPS的速度运行。
